Abstractions for Multi-Sorted Substitutions

### 2023-08-29 paper/paper.tex
Update.

  \subsection{A Structure for Multi-Sorted Syntax}
  The multi-sorted syntax makes it easy to define a structure for
  syntaxes of arbitrary object-languages, i.e.\ syntaxes with
  arbitrary amounts of syntactic categories and variables:
  \LibCode\KTerms
  The first three fields record the definitions of sorts, terms, and variable introduction.
  The last field records that variable introduction
  \ACode{\AField{`\_}} is injective, which is trivially true for
  constructors. The instantiation for our System F syntax is
  straightforward:
  \AppCode\FTerms

@@

  A kit provides the following operations:
  \begin{itemize}
  \item 
    \ACode{\AField{id/`}} converts a variable \ACode{S \ACon{∋} s} into a
    \ACode{S \AField{∋/⊢} s}. For the variable kit, \ACode{S ∋/⊢ s} is instanciated to \ACode{S \ACon{∋} s}, so this
    operation is the identity. For the term kit, \ACode{S ∋/⊢ s} is
    instanciated to \ACode{S \AField{⊢} s}, so this operation is the
    variable constructor \ACode{\AField{`\_}}.
  \item 
    \ACode{\AField{`/id}} converts a \ACode{S ∋/⊢ s} into a term \ACode{S \AField{⊢} s}
    and is dual to the \ACode{\AField{id/`}} operation.
  \item 
    \ACode{\AField{wk}} shifts the DeBruin-Indices in a \ACode{S ∋/⊢ s}.
    The new, unused variable \ACode{\ACon{zero}} can assume any sort \ACode{s'}.
    For variables \ACode{\AField{wk}} is the successor \ACode{\ACon{suc}}.
    For terms \ACode{\AField{wk}} means applying a shifting renaming to the term.
  \end{itemize}

@@

  We first define a \ACode{\ACon{WkKit}}, which captures properties
  between maps and map application, which we could not include in the
  \ACode{\ACon{Kit}} definition, as we already require
  \ACode{\ACon{Kit}}s to define a Traversal. We then create exactly
  two instances of the \ACode{\ACon{WkKit}} for the variable and term
  kit, respectively. Both the structure and the instances are part of
  the library and do not require application code.

@@

  \LibCode\KWkKit
  \LibCode\KWkKitInstances

>>>>

  \subsection{A Structure for Multi-Sorted Syntax}
  The multi-sorted syntax makes it easy to define a structure for
  syntaxes of arbitrary object-languages, i.e.\ syntaxes with
  arbitrary amounts of syntactic categories and variables:
  \LibCode\KSyntax
  The first three fields record the definitions of sorts, terms, and variable introduction.
  The last field records that variable introduction
  \ACode{\AField{`\_}} is injective, which is trivially true for
  constructors. The instantiation for our System F syntax is
  straightforward:
  \AppCode\FSyntaxInst

@@

  A kit provides the following operations:
  \begin{itemize}
  \item 
    \ACode{\AField{id/`}} converts a variable \ACode{S \ACon{∋} s} into a
    \ACode{S \AField{∋/⊢} s}. For the variable kit, \ACode{S ∋/⊢ s} is instanciated to \ACode{S \ACon{∋} s}, so this
    operation is the identity. For the term kit, \ACode{S ∋/⊢ s} is
    instanciated to \ACode{S \AField{⊢} s}, so this operation is the
    variable constructor \ACode{\AField{`\_}}.
  \item 
    \ACode{\AField{`/id}} converts a \ACode{S ∋/⊢ s} into a term \ACode{S \AField{⊢} s}
    and is dual to the \ACode{\AField{id/`}} operation.
  \item 
    \ACode{\AField{wk}} shifts the DeBruin-Indices in a \ACode{S ∋/⊢ s}.
    The new, unused variable \ACode{\ACon{zero}} can assume any sort \ACode{s'}.
    For variables, \ACode{\AField{wk}} is the successor \ACode{\ACon{suc}}.
    For terms, \ACode{\AField{wk}} means applying a shifting renaming to the term.
  \end{itemize}

@@

  In the definition of \ACode{\ACon{Kit}} we required the axiom
  \ACode{\AField{wk-id/`}}, which captured the interaction between
  \ACode{\AField{wk}} and \ACode{\AField{id/`}}:
  \ExampleCode{\KWkId}
  Injecting a variable with \ACode{\AField{id/`}} and then shifting it,
  is the same as injecting a shifted variable.

  Now that we have defined the \ACode{\ACon{Traversal}} structure, we
  can formulate a similar interaction between
  \ACode{\AField{wk}} and \ACode{\AField{`/id}}:
  \ExampleCode{\KIdWk}
  Shifting a variable/term \ACode{x/t} with \ACode{\AField{wk}} and then injecting
  it to a term, is the same as injecting \ACode{x/t} to a term and then applying
  a shifting renaming.

  As this lemma depends on map application \ACode{\ADef{\_⋯\_}} being
  already defined, we cannot add it to the original \ACode{\ACon{Kit}}
  structure, but need to define a new structure for it, which we call
  a \ACode{\ACon{WkKit}}:
  \LibCode\KWkKit

  We then create exactly two instances of the \ACode{\ACon{WkKit}} for
  the variable and term kit, respectively. 
  \LibCode\KWkKitInstances

  Both the structure and the instances are part of the library and do
  not require application code.

@@

  \ExampleCode\KExFourComps
  \ExampleCode\KExTwoComps
  \ExampleCode\KComposition
